Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-16 hscc2017/paper.tex
move section 2.2 to the beginning of the next column
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added Alessandro's comment related to the illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
nudge
keep the standard throughout the text about i.e.
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
space
move title of section 2.2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\renewcommand{\baselinestretch}{0.98}
\allowdisplaybreaks
\include{macros}

@@

By combining and applying state-of-the-art synthesis engines we present a
tool that automatically generates digital controllers for a given continuous
plant model that are correct by construction.  This approach delivers a high
degree of automation, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification.  Specifically, we synthesize stable,
software-implemented embedded controllers along with a model of a physical
plant.  Due to the complexity of such closed-loop systems, in this work we
focus on linear models with known configurations, and perform parametric
synthesis of stabilizing digital controllers (further closed-loop
requirements are left to future work).

@@

The digital controllers synthesized using the algorithm we present in this
paper are typically used in closed loops with continuous (physical) plants. 
Thus, we consider continuous dynamics (the plant) and discrete parts (the
digital controller). In order to obtain an overall model, we discretize the
continuous plant and look at the plant dynamics from the perspective of the digital controller.

@@

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample-and-hold output on the plant, 
with a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$, 
and can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
\end{mylemma}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function $G(z,T)$.
% 
Lemma~\ref{eq:pulsetf} ensures that the poles and zeros match under the
$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term.  This
is sufficient for stability studies over $G(s)$~\cite{fadali}, i.e., if
there is any unstable pole (in the complex domain $\Re\{s\} > 0$), the pulse
transfer function in~\eqref{eq:pulsetf} will also present the same number of
unstable poles ($|z| > 1$)~\cite{Franklin15}.

@@

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
FWL), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using 
$\mathbb R \param {4}{16}$ fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as: 
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
}
\end{equation} 
%
The resulting system, 
%using the typical series loop configuration, 
where $\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
\blue{[check correctness](Notice that this is disregarding further approximation effects on the plant, not accounted for in the reference study.)}   
%\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
%\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
Figure~\ref{fig:original} gives the Bode diagram for the digital controller
represented in~\eqref{Eq:running-example-controller}: 
as the phase margin is negative, 
the controller is unstable when considering the above FWL effects.

>>>>

\renewcommand{\baselinestretch}{0.99}
\allowdisplaybreaks
\include{macros}

@@

By combining and applying state-of-the-art synthesis engines we present a
tool that automatically generates digital controllers for a given continuous
plant model that are correct by construction.  This approach delivers a high
degree of automation, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification.  Specifically, we synthesize stable,
software-implemented embedded controllers along with a model of a physical
plant.  Due to the complexity of such closed-loop systems, in this work we
focus on linear models with known configurations, and perform parametric
synthesis of stabilizing digital controllers (further closed-loop performance
requirements are left to future work).

@@

The digital controllers synthesized using the algorithm we present in this
paper are typically used in closed loops with continuous (physical) plants. 
Thus, we consider continuous dynamics (the plant) and discrete parts (the
digital controller). In order to obtain an overall model for the synthesis, 
we discretize the continuous plant and particularly look at the plant dynamics 
from the perspective of the digital controller.

@@

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample-and-hold output on the plant, 
with a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$, 
and can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
\end{mylemma}
%
In this study, for the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function $G(z,T)$.
% 
Lemma~\ref{eq:pulsetf} ensures that the poles and zeros match under the
$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term.  This
is sufficient for stability studies over $G(s)$~\cite{fadali}, i.e., if
there is any unstable pole (in the complex domain $\Re\{s\} > 0$), the pulse
transfer function in~\eqref{eq:pulsetf} will also present the same number of
unstable poles ($|z| > 1$)~\cite{Franklin15}.

@@

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
FWL), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using 
$\mathbb R \param {4}{16}$ fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as: 
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
}
\end{equation} 
%
The resulting system, 
%using the typical series loop configuration, 
where $\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
Notice that this is disregarding further approximation effects on the plant caused by quantization in the verifier (i.e., $\tilde{G}(z)$).
%\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
%\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
Figure~\ref{fig:original} gives the Bode diagram for the digital controller
represented in~\eqref{Eq:running-example-controller}: 
as the phase margin is negative, 
the controller is unstable when considering the above FWL effects.
